Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-05-14 analysis/paper/paper.Rmd
update fig 4

fig_widths <- c(min = 1.18, single = 3.543, mid = 5.51, two = 7.48)
```

@@

save_plot(here("analysis/figures/Figure1_StudyArea_both.tiff"), 
          out_map,
          dpi = knitr::opts_chunk$get("dpi"),
          base_width = fig_widths["two"], 
          base_height = 6*0.9)
```

@@

tmap_save(tmap_arrange(allMaps, ncol = 3),
          here("analysis/figures/projection_methods_figure.tiff"),
          dpi = 300, height = 8, width = fig_widths["two"])
```

```{r proj-meth-fig, fig.cap="Comparison of road projection method variants (Table 2). The large four sided cutblock in the top right was added to more clearly show algorithm behaviour within cutblocks.The grade penalty method for setting edge weights (top row) encourages roads to follow slope contours, and yields fewer obviously unrealistic 90 degree turns in steep terrain than our simple cost method (middle row). Selecting a single landing at the centroid of each cutblock (bottom left) creates too few roads within cutblocks. In this 1 ha resolution example the Hardy QGIS plugin (bottom middle) creates more curved roads than our simple cost method (middle row), and does not follow slope contours like the grade penalty method (top row). Landing density is high for all except the centroid and Hardy variants."}
knitr::include_graphics(here("analysis/figures/projection_methods_figure.tiff"))
```

@@

knitr::include_graphics(here("analysis/figures/Figure4_map_update.png"))

>>>>

fig_widths <- c(min = 1.18, single = 3.48, mid = 5.51, two = 7.16)
```

@@

save_plot(here("analysis/figures/Figure1_StudyArea_both.tiff"), 
          out_map,
          compression = "lzw",
          dpi = knitr::opts_chunk$get("dpi"),
          base_width = fig_widths["two"], 
          base_height = 6*0.9)
```

@@

tmap_save(tmap_arrange(allMaps, ncol = 3),
          here("analysis/figures/projection_methods_figure.tiff"),
          dpi = 300, compression="lzw", 
          height = 8, width = fig_widths["two"])
```

```{r proj-meth-fig, fig.height=8, fig.width=fig_widths["two"], fig.cap="Comparison of road projection method variants (Table 2). The large four sided cutblock in the top right was added to more clearly show algorithm behaviour within cutblocks.The grade penalty method for setting edge weights (top row) encourages roads to follow slope contours, and yields fewer obviously unrealistic 90 degree turns in steep terrain than our simple cost method (middle row). Selecting a single landing at the centroid of each cutblock (bottom left) creates too few roads within cutblocks. In this 1 ha resolution example the Hardy QGIS plugin (bottom middle) creates more curved roads than our simple cost method (middle row), and does not follow slope contours like the grade penalty method (top row). Landing density is high for all except the centroid and Hardy variants."}
knitr::include_graphics(here("analysis/figures/projection_methods_figure.tiff"))
```

@@

knitr::include_graphics(here("analysis/figures/Figure4_map_update.tif"))
